% status: 2
% chapter: Security

\title{Financial Analysis Service}

\author{Rashmi Ray}
\affiliation{%
  \institution{Indiana University}
  \streetaddress{107 S. Indiana Avenue}
  \city{Bloomington}
  \state{Indiana}
  \postcode{43017-6221}
}
\email{rashray@iu.edu}
% The default list of authors is too long for headers}

\renewcommand{\shortauthors}{Uma Kugan}

\begin{abstract}
The project involves creating a Kubernete cluster in GoogleCloud and later 
automating the installation and setup process by including the shell script.
The same process will be executed in a Kubernetes Chameleon cluster. The shell
script will be modified as needed. The project will also involve developing a stock 
API using flask that will provide real-time analysis of the stock market data. The performance
of the API will be compared in both Chameleon and GoogleCloud. The stock API will 
be using python, pyGal, Quandl. The benchmarking process will be registered in the project report.

\end{abstract}

\keywords{hid-sp18-417, Kubernetes, deloyment, performance}


\maketitle

\section{Introduction}
The area of research for this project is Kubernetes. Looking at the high popularity of 
the tool, it is becoming a buzz word in the world of cloud computing and containers. 
The project compares and contrasts the ease of deployment, configuration and performance 
in different systems. Before going into the detail of the project outcome, it is important
to introduce several key components of the project.

\subsection{Kubernetes}
Kubernetes is an open-source system developed and maintained by Google Inc. The system 
provides a container orchestration platform for ease of deployment, management and scaling 
of services and resources. The system places containers automatically based on it resource 
requirement not compromising availability. Similarly, it provides seamless management of 
data volumes and storage system. It allows updating configurations of the deployment without 
rebuilding the image. The system can facilitate public, private or hybrid container management 
system based on an organization’s requirement.  Kubernetes resource monitoring system oversees 
automatic rollout and rollback of the resources in case of fallbacks.


Kubernetes is also known as K8 or kube. This is originally developed based on Google’s container 
management system. A Kubernetes can be deployed in a single host, but it is designed to be
benefitted efficiently when used for a cluster of connected hosts. Use of a cluster of 
multiple hosts facilitates high availability.


The primary components of the system are: 

The master node controls the other nodes. Nodes are the hosts in the cluster. Pod is a group 
of one or more containers deployed in a node.  The Replication Controller monitors and controls
the replicas of the services. A Kubernetes service is a single unit that has a collection of 
rules/configuration for effective deployment of a container. Various metadata such as replicas,
environment, track, port, can be defined in a service configuration. Kubectl is the command line 
configuration tool provided by Kubernetes. 


\subsection{Google Kubernetes Engine [GKE]}
\TODO{GoogleCLoud setup and configuration is discussed in the context of the project}

\subsection{Python API}
\TODO{Python API control structure and available features are discussed}

\subsection{Flask Service}
\TODO{the details of the swagger service in use}

\subsection{setup process}
\TODO{Initial setup experience is discussed}

\subsection{Chameleon}
\TODO{JetStream setup is discussed.}

\subsection{Stocks Analysis}
\TODO{Practice use of the webservice and the current 
market trend of tools and technologies in the context is discussed.}

\subsection{Trouble shooting}
\TODO{Troubleshooting experience during the project is logged}

\subsection{BenchMarking}
\TODO{Compare and contrast the installation, setup and performance of the service in Pi and Jetstream cluster}


\section{Conclusion}

\TODO{Put here an conclusion.} Conclusion and abstracts must not have any
citations in the section.


\begin{acks}
The author would like to thank Dr. Gregor von Laszewski for his support and 
suggestions in writing this paper.
\end{acks}

\bibliographystyle{ACM-Reference-Format}
\bibliography{report}



