% status: 0
% chapter: TBD

\title{Apache CloudStack an Overview}


\author{Rashmi Ray}
\affiliation{%
  \institution{Indiana University}
  \streetaddress{}
  \city{Bloomington} 
  \state{IN} 
  \postcode{47408}
}
\email{rashray@iu.edu}

\author{Gregor von Laszewski}
\affiliation{%
  \institution{Indiana University}
  \streetaddress{Smith Research Center}
  \city{Bloomington} 
  \state{IN} 
  \postcode{47408}
  \country{USA}}
\email{laszewski@gmail.com}


% The default list of authors is too long for headers}
\renewcommand{\shortauthors}{G. v. Laszewski}


\begin{abstract}
In this ever-evolving age of cloud computing, it’s important for organizations to adopt the right
cloud orchestration tool to support the rapid growth of their infrastructure. Ease of scalability, robust research-base
for future growth and current large userbase also facilitates the process. CloudStack can be the 
answer here. Apache CloudStack is a top level project from Apache, so it indeed has a support of a solid team of researchers.

\end{abstract}

\keywords{hid-sp18-417, CloudStack, apache, cloud architecture, cloud technology, i516}

\maketitle

\section{Introduction}
‘‘Apache CloudStack is open source software designed to deploy and manage large networks of 
virtual machines, as a highly available, highly scalable Infrastructure as a Service (IaaS)
cloud computing platform. CloudStack is used by a number of service providers to offer public 
cloud services, and by many companies to provide an on-premises (private) cloud offering, 
or as part of a hybrid cloud solution.’’~\cite{hid-sp18-417-www-cloudstack-intro}. 
Infrastructure as a Service[IaaS] is kind of cloud computing service that enables cloud 
configuration over the internet. 


\section{History}
The CloudStack was originally developed by cloud.com formerly know as VMOs. 
The project started in 2008 and was released under GNU general public license. 
In Jul 2011 Citrix purchased the software and released it again. In 2012 Citrix 
renewed CloudStack licensed under the Apache and later donated the project to Apache.
Since then The tool has graduated from Apache incubator and released in Mar 2013. 


\section{Key Features}
{\bf Hypervisor Support: } A hypervisor or Virtual Machine Monitor is a software or firmware that creates 
and runs virtual machines. CloudStack currently supports most of the major hypervisors.  CloudStack enables 
a single cloud to constitute of multiple types of hypervisor implementations. This is considered a key 
advantage when implementing CloudStack on an existing infrastructure to enable maximum use of the existing 
resources. {\bf Massively Scalable:} CloudStack can manage tens of thousands of physical servers installed
in geographically distributed datacenters. The management server scales near-linearly eliminating the need for
cluster-level management servers. Maintenance or other outages of the management server can occur without
affecting the virtual machines running in the cloud ~\cite{hid-sp18-417-www-cloudstack-scalability}. 
{\bf High Availability:} CloudStack provides features to increase availability. It enables the management server 
deployed across multiple nodes, this increasing availability through load balancing. MYSQL can be configured
simulate a replication that can serve as a fallback in case of data loss. The tool also provides a {\bf robust rest API} 
for operation and management of the cloud. The API can be used with a CloudStack system as the underlying server. 
The software also provides Amazon Web Services compatible API. CloudStack provides an EC2 API translation layer
to permit the common EC2 tools to be used in the use of a CloudStack cloud. ~\cite{hid-sp18-417-www-cloudstack-aws}
The tool also eases configuration management, Hypervisor agnostic, user management, snapshot management and 
networking resource optimization. 
{\bf GUI: } It might not be a prominent advantage for the cloud computing community as it mostly prefers to carryout 
instruction in the console, but for occasional users it’s an added benefit that CloudStack provides an efficient 
customizable Graphical User Interface. In all CloudStack provides a comprehensive package of features that can enable 
an organization to deploy a full featured cloud Infrastructure.

\section{Terminology}

\section{Deployment Architecture}
To use CloudStack, several deployment architectures can be adopted depending on the cloud requirements of an
organization. The strength of the deployment can range from a single machine to thousands of nodes spread across the 
globe in several data centers several networking technologies. A CloudStack deployment primarily consists of a
management server and set of resources [IP addresses, VLANs, storage systems] to constitute the cloud.   For simplest form of deployment, only one single machine can be used to serve both as 
the management server and hypervisor host. The same system can be scaled to feed increased demand to spread across 
multiple management servers to support larger userbase and facilitate better load balancing. The management server 
typically runs on a dedicated machine or as a virtual machine. It controls allocation of virtual machines to hosts a
nd assigns storage and IP addresses to the virtual machine instances. The Management Server runs in an Apache Tomcat 
container and requires a MySQL database for persistence. ~\cite{hid-sp18-417-www-cloudstack-management-server}



\section{Growth}

\section{Conclusion}

\begin{acks}

  The author would like to thank Dr.~Gregor~von~Laszewski for his
  support and suggestions to write this paper.

\end{acks}

\bibliographystyle{ACM-Reference-Format}
\bibliography{report} 
